---
title: "MixedeffectsAnalysis"
output: html_document
date: "2022-09-13"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mixed effect models

```{r cars}
library(ggeffects)
library(lme4)
library(ggplot2)
P1<-read.csv("data_P1_TpR.csv")
P1<-P1[P1$Game!=1,]
P2<-read.csv("data_P2_TpR.csv")
P2<-P2[P2$Game!=1,]
P1_sd<-read.csv("data_P1_SD.csv")
P2_sd<-read.csv("data_P2_SD.csv")

P2_sd<-P2_sd[P2_sd$Game!=1,]
P1_sd<-P1_sd[P1_sd$Game!=1,]
P2_sd$Time <- P2$Time
P1_sd$Time <- P1$Time

P1<-P1[!P1$Target=="Hello World",]
P2<-P2[!P2$Target=="Hello World",]
P1_sd<-P1_sd[!P1_sd$Target=="Hello World",]
P2_sd<-P2_sd[!P2_sd$Target=="Hello World",]


```

## Plot of Rounds against Time per round
### Only using data from headset 1

```{r pressure11}

ggplot(data=P1, aes(x=Game, y=Time, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)

```

## Plot of rounds against standard deviation of x 
### Only using data from director (both headsets)
```{r pressure12}
P_sd = rbind(P1_sd, P2_sd)
P_sd = P_sd[P_sd$Role == "director",]
P_sd<-P_sd[P_sd$Game!=1,]

ggplot(data=P_sd, aes(x=Game, y=X, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)

ggplot(data=P_sd, aes(x=Game, y=Y, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)


ggplot(data=P_sd, aes(x=Game, y=Z, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)

```

## Plot of rounds against standard deviation of y 
### Only using data from director (both headsets)
```{r pressure122}

ggplot(data=P_sd, aes(x=Game, y=Y, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)

```

## Plot of rounds against standard deviation of z 
### Only using data from director (both headsets)
```{r pressure32}
ggplot(data=P_sd, aes(x=Game, y=Z, color=Condtion)) +
  geom_point(position=position_dodge(width=0.3))+geom_smooth(method = "loess", se = TRUE)
```


## Plot of rounds against success

```{r pressure13}
P_sd<-P_sd[P_sd$Game!=1,]
P2_sd_norm = P_sd[P_sd$Condtion == "normal",]
P2_sd_nmod = P_sd[P_sd$Condtion == "modified",]

P2_sd_norm$Succes <- as.factor(P2_sd_norm$Succes )
P2_sd_nmod$Succes <- as.factor(P2_sd_nmod$Succes )

#Modified
cdplot(Succes ~ Game, data=P2_sd_nmod)

#Normal
cdplot(Succes ~ Game, data=P2_sd_norm)


```

## Plot of words introducer/non introducer against z
### Only modified group

```{r pressure14}
P <- rbind(P2_sd,P1_sd)
P <- P[P$Role=="director",]
P <- P[P$Condtion=="modified",]
P<-P[!P$Target=="Hello World",]
P<-P[P$Game!=1,]

D<-paste0(P$Target, P$Introducer)

ggplot(data=P, aes(x=D, y=Z, color=Introducer)) +
  geom_point(position=position_dodge(width=0.3))+theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))



```




## Compared baseline model with model of condition on success

```{r pressure}
success <- as.numeric(P2_sd$Success)
condition<-as.factor(P2_sd$Condtion)
TIME <-round(P2_sd$Time/1000)
PAIR <- as.factor(P2_sd$Pair)
TARGET<- as.factor(P2_sd$Target)
IsIntroducer <-as.factor(P2_sd$Introducer)
GAME<- P2_sd$Game
sdz<-P2_sd$Z
sdx<-P2_sd$X
sdy<-P2_sd$Y


model1 = glmer( success ~ 1  + (1|PAIR) + (1| TARGET),family = binomial(link = "logit"))
model2err = glmer( success ~ condition + (1+condition|PAIR) + (1+condition|TARGET), family = binomial(link = "logit"), control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))

model2 = glmer( success ~ condition + (1+condition|TARGET), family = binomial(link = "logit"))
summary(model2)
AIC(model1,model2)

```









```{r pressure3}
library(ggplot2)
library(ggeffects)
library(lme4)
P1<-read.csv("data_P1_TpR.csv")
P2<-read.csv("data_P2_TpR.csv")

P1_sd<-read.csv("data_P1_SD.csv")

P2_sd<-read.csv("data_P2_SD.csv")
P2_sd$Time <- P2$Time



P2_sd$Time <- P2$Time
P1_sd$Time <- P1$Time
P <- rbind(P2_sd,P1_sd)

P <- P[P$Role=="director",]
P<-P[P$Target!="Hello World",]
P<-P[P$Game!=1,]


success <- as.numeric(P$Success)
condition<-as.factor(P$Condtion)
TIME <-round(P$Time/1000)
PAIR <- as.factor(P$Pair)
TARGET<- as.factor(P$Target)
IsIntroducer <-as.factor(P$Introducer)
PARTICIPANT <- as.factor(P$Participant)
sdz<-P$Z
sdx<-P$X
sdy<-P$Y
Game <- P$Game
Win <-as.factor(P$Success)
```


## Mixed effect models of all axis over time 


```{r pressure2}
lmodel1A =  lmer (sdz ~   1  + (1 | PARTICIPANT)+ (1 | TARGET) + (1|PAIR))
lmodel1B =  lmer (sdz ~   Game  + (Game| PARTICIPANT)+ (Game | TARGET) + (Game|PAIR),control = lmerControl(
                           optimizer ='optimx', optCtrl=list(method='L-BFGS-B')) )
AIC(lmodel1A,lmodel1B)
summary(lmodel1B)

lmodel2A =  lmer (sdx ~    1  + (1 | PARTICIPANT)+ (1 | TARGET) + (1|PAIR))
lmodel2B =  lmer (sdx ~  Game  + (Game | PARTICIPANT)+ (Game | TARGET) + (Game|PAIR),control = lmerControl(
                           optimizer ='optimx', optCtrl=list(method='L-BFGS-B')))
AIC(lmodel2A,lmodel2B )
summary(lmodel2B)

lmodel3A =  lmer (sdy ~    1  + (1 | PARTICIPANT)+ (1 | TARGET) + (1|PAIR))
lmodel3B =  lmer (sdy ~   Game  + (Game | PARTICIPANT) + (Game | TARGET) + (Game|PAIR),control = lmerControl(
                           optimizer ='optimx', optCtrl=list(method='nlminb')))
AIC(lmodel3A,lmodel3B )
summary(lmodel3B)

model1Bgraph = ggpredict(lmodel1B,c("Game"))
plot(model1Bgraph)
model2Bgraph = ggpredict(lmodel2B,c("Game"))
plot(model2Bgraph)
model3Bgraph = ggpredict(lmodel3B,c("Game"))
plot(model3Bgraph)


```


## Target and introducer as fixed variable dependend is axis.


```{r pressure4}
lmodel1A =  lmer (sdz ~   1  + (1 | PARTICIPANT) + (1|PAIR))
lmodel1B =  lmer (sdz ~   TARGET+ IsIntroducer + (1 | PARTICIPANT)+(1+TARGET+ IsIntroducer|PAIR ))
AIC(lmodel1A,lmodel1B)
model1Bgraph = ggpredict(lmodel1B,c("TARGET"))
plot(model1Bgraph)
model1Bgraph = ggpredict(lmodel1B,c("IsIntroducer"))
plot(model1Bgraph)
summary(lmodel1B)


lmodel2A =  lmer (sdx ~   1 + (1 | PARTICIPANT) + (1|PAIR))
lmodel2B =  lmer (sdx ~   TARGET+IsIntroducer + (1 | PARTICIPANT)+(1+TARGET+ IsIntroducer|PAIR ))
model2Bgraph = ggpredict(lmodel2B,c("TARGET"))
plot(model2Bgraph)
model2Bgraph = ggpredict(lmodel2B,c("IsIntroducer"))
plot(model2Bgraph)
summary(lmodel2B)

lmodel3A =  lmer (sdy ~   1  + (1 | PARTICIPANT) + (1|PAIR))
lmodel3B =  lmer (sdy ~   TARGET+IsIntroducer  + (1 | PARTICIPANT) +(1+TARGET+ IsIntroducer|PAIR ))
model3Bgraph = ggpredict(lmodel3B,c("TARGET"))
plot(model3Bgraph)
model3Bgraph = ggpredict(lmodel3B,c("IsIntroducer"))
plot(model3Bgraph)
summary(lmodel3B)


```

## Target and introducer as fixed variable dependend is axis.


```{r pressure4}
lmodel1A =  lmer (sdz ~   1  + (1 | PARTICIPANT) + (1|PAIR))
lmodel1B =  lmer (sdz~condition+ (1 | PARTICIPANT) +(1|PAIR)+(condition|TARGET))
AIC(lmodel1A,lmodel1B)
model1Bgraph = ggpredict(lmodel1B,c("condition"))
plot(model1Bgraph)
summary(lmodel1B)


lmodel2A =  lmer (sdx ~   1 + (1 | PARTICIPANT) + (1|PAIR))
lmodel2B =  lmer (sdx~condition+ (1 | PARTICIPANT) +(1|PAIR)+(condition|TARGET))
model2Bgraph = ggpredict(lmodel2B,c("condition"))
plot(model2Bgraph)
summary(lmodel2B)
AIC(lmodel2A,lmodel2B)

lmodel3A =  lmer (sdy ~   1  + (1 | PARTICIPANT) + (1|PAIR))
lmodel3B =  lmer (sdy~condition+ (1 | PARTICIPANT) +(1|PAIR)+(condition|TARGET))
model3Bgraph = ggpredict(lmodel3B,c("condition"))
plot(model3Bgraph)
summary(lmodel3B)
AIC(lmodel3A,lmodel3B)


```

## Target and introducer as fixed variable dependend is axis.


```{r pressure4}
P2_sd<-P2_sd[!P2_sd$Game==1,]
P1_sd<-P1_sd[!P1_sd$Game==1,]
P_mod <-P[P$Condtion=="modified",]

P_mod$Introducer = as.factor(P_mod$Introducer)
lmodel1A =  lmer (Z ~   1  + (1 | Participant) + (1|Pair)+ (1|Target),data = P_mod)
lmodel1B =  lmer (Z ~   Introducer  + (Introducer | Participant) + (Introducer|Pair)+ (Introducer|Target),data = P_mod)

AIC(lmodel1A,lmodel1B)
model1Bgraph = ggpredict(lmodel1B,c("Introducer"))
plot(model1Bgraph)
summary(lmodel1B)


lmodel2A =  lmer (X ~   1  + (1 | Participant) + (1|Pair)+ (1|Target),data = P_mod)
lmodel2B =  lmer (X ~   Introducer  + (Introducer | Participant) + (Introducer|Pair)+ (Introducer|Target),data = P_mod)
model2Bgraph = ggpredict(lmodel2B,c("Introducer"))
plot(model2Bgraph)
summary(lmodel2B)
AIC(lmodel2A,lmodel2B)

lmodel3A =  lmer (Y ~   1  + (1 | Participant) + (1|Pair)+ (1|Target),data = P_mod)
lmodel3B =  lmer (Y ~   Introducer  + (Introducer | Participant) + (Introducer|Pair)+ (Introducer|Target),data = P_mod)
model3Bgraph = ggpredict(lmodel3B,c("Introducer"))
plot(model3Bgraph)
summary(lmodel3B)
AIC(lmodel3A,lmodel3B)


```


