---
title: "Report"
output:
  pdf_document: default
  html_document: default
date: "2022-09-19"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Mixed-effect models
### Here are some mixed effect of the data collected from the VR experiments

Effects:

--> IsIntroducer: If this is the first time the director is seeing the target

--> TIME: The duration of the game

--> PAIR: Pair number

--> TARGET: Target word that needs to be guessed

--> GAME: Game number

--> condition: modified or normal

--> PARTICIPANT: each individual



```{r cars, echo=FALSE}
library(ggplot2)
library(ggeffects)
library(lme4)
P1<-read.csv("data_P1_TpR.csv")
P2<-read.csv("data_P2_TpR.csv")

P1_sd<-read.csv("data_P1_SD.csv")

P2_sd<-read.csv("data_P2_SD.csv")
P2_sd$Time <- P2$Time



P2_sd$Time <- P2$Time
P1_sd$Time <- P1$Time
P <- rbind(P2_sd,P1_sd)

#P <- P[P$Condtion=="modified",]
P <- P[P$Role=="director",]

D<-paste0(P$Target, P$Introducer)

success <- as.numeric(P$Success)
condition<-as.factor(P$Condtion)
TIME <-round(P$Time/1000)
PAIR <- as.factor(P$Pair)
TARGET<- as.factor(P$Target)
IsIntroducer <-as.factor(P$Introducer)
PARTICIPANT <- as.factor(P$Participant)
sdz<-P$Z
sdx<-P$X
sdy<-P$Y
Game <- P$Game
Win <-as.factor(P$Success)

```

## Standard deviation

### These linear mixed-effect models investigates the effect of condition on the standard deviation of the z-axis and the x-axis.

```{r pressure}
lmodel2B =  lmer (sdz ~   condition + (condition|PAIR) + (1 | PARTICIPANT) + (condition|TARGET))
AIC(lmodel2B)
model2Bgraph = ggpredict(lmodel2B,c("condition"))
plot(model2Bgraph)

lmodel2C =  lmer (sdx ~   condition + (condition|PAIR) + (1 | PARTICIPANT) +(condition|TARGET))
AIC(lmodel2C)
model2Cgraph = ggpredict(lmodel2C,c("condition"))
plot(model2Cgraph)
```


### Because I switched the x-axis with the z-axis in the modified group, I also want to see if more movement on the z-axis is caused by less movement on the x-axis ( for the modified group):

```{r pressure2}
lmodel12 =  lmer (sdz ~   sdx*condition + (sdx*condition|PAIR) + (1 | PARTICIPANT) + (sdx*condition|TARGET))

AIC(lmodel12)
model12graph = ggpredict(lmodel12,c("sdx","condition"))
plot(model12graph)
```

### I also checked the effect that introducer have on the the z-axis (in combination with other fixed effect like Win and condition) :

```{r pressure22}
lmodel =  lmer (sdz ~   IsIntroducer + (IsIntroducer|PAIR) + (1 | PARTICIPANT) + (IsIntroducer|TARGET))
lmodel3 =  lmer (sdz ~   condition+IsIntroducer + (condition+IsIntroducer|PAIR) + (1 | PARTICIPANT) + (condition+IsIntroducer|TARGET))
lmodel4 =  lmer (sdz ~   condition*IsIntroducer + (condition*IsIntroducer|PAIR) + (1 | PARTICIPANT) + (condition*IsIntroducer|TARGET))
lmodel5 =  lmer (sdz ~   Win + (Win|PAIR) + (1 | PARTICIPANT) + (Win|TARGET))
lmodel6 =  lmer (sdz ~   Win+IsIntroducer + (Win+IsIntroducer|PAIR) + (1 | PARTICIPANT) + (Win+IsIntroducer|TARGET))
lmodel7 =  lmer (sdz ~   Win*IsIntroducer + (Win*IsIntroducer|PAIR) + (1 | PARTICIPANT) + (Win*IsIntroducer|TARGET))


AIC(lmodel,lmodel3,lmodel4,lmodel5,lmodel6,lmodel7)

#Model lmodel7 seems to be the best performing model, based on the AIC score.
modelgraph = ggpredict(lmodel6,c("IsIntroducer"))
plot(modelgraph)
modelgraph = ggpredict(lmodel6,c("Win"))
plot(modelgraph)
```




```{r pressure3}
P1<-read.csv("data_P1_TpR.csv")
P2<-read.csv("data_P2_TpR.csv")

P1_sd<-read.csv("data_P1_SD.csv")

P2_sd<-read.csv("data_P2_SD.csv")
P2_sd$Time <- P2$Time

success <- as.numeric(P2_sd$Success)
condition<-as.factor(P2_sd$Condtion)
TIME <-round(P2_sd$Time/1000)
PAIR <- as.factor(P2_sd$Pair)
TARGET<- as.factor(P2_sd$Target)
IsIntroducer <-as.factor(P2_sd$Introducer)
GAME<- P2_sd$Game
sdz<-P2_sd$Z
sdx<-P2_sd$X
sdy<-P2_sd$Y

```

## Success

### Here are some models attempting to predict the success rate using various fixed effects

```{r pressure4, warning=FALSE,message=FALSE}
model9 = glmer( success ~ IsIntroducer+TIME + (IsIntroducer+TIME|PAIR) + (IsIntroducer+TIME|TARGET),family = binomial(link = "logit"),control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
model8 = glmer( success ~ IsIntroducer + (IsIntroducer|PAIR) + (IsIntroducer|TARGET),family = binomial(link = "logit"),control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
model7 = glmer( success ~ GAME*TIME + (GAME*TIME|PAIR) + (GAME*TIME|TARGET),family = binomial(link = "logit"),control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
model6 = glmer( success ~ GAME+TIME + (GAME+TIME|PAIR) + (GAME+TIME|TARGET),family = binomial(link = "logit"))
model5 = glmer( success ~ GAME + (GAME|PAIR) + (GAME|TARGET),family = binomial(link = "logit"))
model5b = glmer( success ~ GAME+IsIntroducer+ (GAME+IsIntroducer|PAIR) + (GAME+IsIntroducer|TARGET),family = binomial(link = "logit"))
model4 = glmer( success ~ condition * TIME + (condition*TIME|PAIR) + (condition *TIME| TARGET), control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')), family = binomial(link = "logit"))
model3 = glmer( success ~ condition + TIME + (condition+TIME|PAIR) + (condition +TIME| TARGET), control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')),  family = binomial(link = "logit"))
model2B = glmer( success ~ condition + (condition|TARGET), family = binomial(link = "logit"))
model2 = glmer( success ~ TIME + (TIME|PAIR) + (TIME|TARGET),family = binomial(link = "logit"), control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
model1 = glmer( success ~ 1  + (1|PAIR) + (1| TARGET),family = binomial(link = "logit"), control = glmerControl(optimizer ='optimx', optCtrl=list(method='nlminb')))
AIC(model1,model2,model2B,model3,model4,model5,model5b,model6,model7,model8,model9)

model2graph = ggpredict(model2,c(" TIME"))
plot(model2graph)

model8graph = ggpredict(model8,c("IsIntroducer"))
plot(model8graph)

model5graph = ggpredict(model5,c("GAME"))
plot(model5graph)

model2Bgraph = ggpredict(model2B,c("condition"))
plot(model2Bgraph)
```

